---
title: "HW2_tianjiang"
author: "Tian Jiang"
date: "9/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 3

* Making my life easier in the long run.
* Making others appreciate my work.

# Problem 4

Note. There are warnings of "NAs generated" in the cleaning process. But I removed the NAs in the following process so the results were not influenced. Thanks!

```{r}
install.packages("dplyr")
install.packages("tidyr")
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
```
## a. A Sensory data from five operators  

### Cleaning 2X 
After this step, no outliers were found.
```{r}
sensory <- read.delim("http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/Sensory.dat")

#Base
sensory1 <- data.frame(lapply(sensory, as.character), stringsAsFactors=FALSE)
sensorylist <- strsplit(sensory1$X," ")
sensorylist2<-{}
for (i in 1:length(sensorylist))
{sensorylist1<-unlist(sensorylist[i])
 if (length(sensorylist1)>5)
    {sensorylist1<-sensorylist1[-1]}
     sensorylist2<-rbind(sensorylist2,sensorylist1)
}
sensory7<-as.data.frame(sensorylist2)
my_vector <- c(1)
for (i in 1:10)
{my_vector1 <- rep(i,3)
 my_vector<-c(my_vector,my_vector1)}
sensory7<-cbind(my_vector,sensory7)
sensory7 <- sensory7[-c(1), ] 
colnames(sensory7) <- c("item","Operator1", "Operator2","Operator3","Operator4","Operator5")
sensory7<-as.data.frame(sensory7)
row.names(sensory7)<-c(1:30)
#sensory7

#Tidyverse
sensory<-sensory %>% separate(col = X, into = c("1","2","3","4","5","6"), sep = " ") %>% select(-Operator)
sensory2<-sensory[-1,]
for (i in 1:30)
{if ((i %% 3)!=1)
    {for (j in 2:6)
         sensory2[i,8-j]<- sensory2[i,8-j-1]
         sensory2[i,1]<-sensory2[i-1,1]
     }
 }
colnames(sensory2) <- c("item","Operator1", "Operator2","Operator3","Operator4","Operator5")
row.names(sensory2)<-c(1:30)
sensory8<-as.data.frame(sensory2)
t<-(sensory8)
sensory8=matrix(unlist(t(t)), byrow=T,30,6)
colnames(sensory8) <- c("item","Operator1", "Operator2","Operator3","Operator4","Operator5")
class(sensory8) <- "numeric"
df <- as_tibble(sensory8)    
#df
```

### Summary Table
Because no obvious outliers in the initial dataset were found, a table summarsing mean values of every item by each operator was built. Medians or ranges were not summarised because the numerical difference is not large in this dataset. But they would be calculated in the next question. 
```{r}
table<-df %>% group_by(item) %>% summarize(MeanOfOperator1 = mean(Operator1),MeanOfOperator2 = mean(Operator2),MeanOfOperator3 = mean(Operator3),MeanOfOperator4 = mean(Operator4),MeanOfOperator5 = mean(Operator5))
table
table1<-(cbind(table,rowMeans(table)))
table2<-cbind(table1[,1],table1[,7])
colnames(table2)<-c("item","Meanof5Operators")
table2 <- as_tibble(table2)   
class(table2$item)<-"character"
table2
```
### Plot
From the plot we see Item 9 got highest values with all of the 5 operators. And the values for a certain item among 5 operators don't vary much. For future endeavors, I'll also compare behaviors of data derived each time because there 3 sets of values for each item.
```{r}
DF <- data.frame(item = c("1", "2", "3","4","5","6","7","8","9","10"),
                 Operator1 = c(table$MeanOfOperator1),
                 Operator2 = c(table$MeanOfOperator2),
                 Operator3 = c(table$MeanOfOperator3),
                 Operator4 = c(table$MeanOfOperator4),
                 Operator5 = c(table$MeanOfOperator5))
DFtall <- DF %>% gather(key = Operator, value = Value, Operator1:Operator5)
plot<-ggplot(DFtall, aes(Operator, Value, fill =item)) + geom_col(position = "dodge")
plot

plot1<-ggplot(table2, aes(item, Meanof5Operators, fill =item)) + geom_col(position = "dodge")
plot1
```


## b. Gold Medal performance for Olympic Men's Long Jump
### Cleaning 2X No outlier detected
```{r}
LongJumpData <- read.delim("http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat")

#Base
LongJumpData1 <- data.frame(lapply(LongJumpData, as.character), stringsAsFactors=FALSE)
LongJumpDatalist <- strsplit(LongJumpData1$Year.Long.Jump.Year.Long.Jump.Year.Long.Jump.Year.Long.Jump," ")
LongJumpDataframe<-as.data.frame(LongJumpDatalist[1:4])
t<-t(LongJumpDataframe)
LongJumpDatamatrix1=matrix(unlist(t(t)), byrow=T, 16, 2)
LongJumpDataframe<-as.data.frame(LongJumpDatalist[5:6])
t<-t(LongJumpDataframe)
LongJumpDatamatrix2=matrix(unlist(t(t)), byrow=T, 6, 2)
df6<-rbind(LongJumpDatamatrix1,LongJumpDatamatrix2)
colnames(df6) <- c("Year","Score")
class(df6) <- "numeric"

#Tidyverse
colnames(LongJumpData) <- c("X")
LongJumpData1<-LongJumpData %>% separate(col=X,into=c("1","2","3","4","5","6","7","8"),sep = " ")
df1 <-LongJumpData1 %>% select(1, 2)
df2 <-LongJumpData1 %>% select(3, 4)
colnames(df2) <- c("1","2")
df3 <-LongJumpData1 %>% select(5, 6)
colnames(df3) <- c("1","2")
df4 <-LongJumpData1 %>% select(7, 8)
colnames(df4) <- c("1","2")
df5<-rbind(df1,df2,df3,df4)
colnames(df5) <- c("Year","Score")
df5<-drop_na(df5)
sensory8<-as.data.frame(df5)
t<-(sensory8)
sensory8=matrix(unlist(t(t)), byrow=T,22,2)
colnames(sensory8) <- c("Year","Score")
class(sensory8) <- "numeric"
df <- as_tibble(sensory8)
df[,1]<-df[,1]+1900
```
### Summary Table
```{r}
table<-df %>%  summarize(MaxScore = max(Score),MinScore = min(Score),MeanScore = mean(Score),MedianScore = median(Score))
table
```
### Plot
```{r}
plot(df$Year,df$Score, type="l", col="green", lwd=5, xlab="Year", ylab="Score", main="Long Jump Men")
```


## c. Brain weight (g) and body weight (kg) for 62 species 
### Issues 
Different species can have very different scales of weights. But the meaningful thing to do is to look at the Brain-Body weight ratio of every species.
### Cleaning 2X
```{r}
weightData <- read.delim("http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat")

#Base
weightData1 <- data.frame(lapply(weightData, as.character), stringsAsFactors=FALSE)
weightDatalist <- strsplit(weightData1$Body.Wt.Brain.Wt.Body.Wt.Brain.Wt.Body.Wt.Brain.Wt," ")
weightDataframe<-as.data.frame(weightDatalist[1:20])
t<-t(weightDataframe)
weightDatamatrix1=matrix(unlist(t(t)), byrow=T, 60, 2)
weightDataframe<-as.data.frame(weightDatalist[21])
t<-t(weightDataframe)
weightDatamatrix2=matrix(unlist(t(t)), byrow=T, 2, 2)
weight<-rbind(weightDatamatrix1,weightDatamatrix2)
colnames(weight) <- c("Body.Wt","Brain.Wt")
class(weight) <- "numeric"

#Tidyverse
colnames(weightData) <- c("X")
weightData1<-weightData %>% separate(col=X,into=c("1","2","3","4","5","6"),sep = " ")
df1 <-weightData1 %>% select(1, 2)
df2 <-weightData1 %>% select(3, 4)
colnames(df2) <- c("1","2")
df3 <-weightData1 %>% select(5, 6)
colnames(df3) <- c("1","2")
df5<-rbind(df1,df2,df3)
colnames(df5) <- c("Body.Wt","Brain.Wt")
df5<-drop_na(df5)
sensory8<-as.data.frame(df5)
t<-(sensory8)
sensory8=matrix(unlist(t(t)), byrow=T,62,2)
colnames(sensory8) <- c("Body.Wt","Brain.Wt")
class(sensory8) <- "numeric"
df <- as_tibble(sensory8)
df$Ratio<-(df$Brain.Wt)*0.001/(df$Body.Wt)
```
### Summary Table
```{r}
table<-df %>%  summarize(Max = max(Body.Wt),Min = min(Body.Wt),Mean = mean(Body.Wt),Median = median(Body.Wt))
table1<-df %>%  summarize(Max = max(Brain.Wt),Min = min(Brain.Wt),Mean = mean(Brain.Wt),Median = median(Brain.Wt))
table2<-df %>%  summarize(Max = max(Ratio),Min = min(Ratio),Mean = mean(Ratio),Median = median(Ratio))
Variable<-c("Body.Wt/kg","Brian.Wt/g","Ratio")
a<-rbind(table,table1,table2)
FinalTable<-cbind(Variable,a)
FinalTable
```
### A valuable plot
The ratios for 50% of the species are between about 0.005 and 0.015. Only 2 of them are larger than 0.03. We could further explore if the 2 species have higher IQ.
```{r}
boxplot(df$Ratio,main = "Brain-Body Ratio")
```


## d. Triplicate measurements of tomato yield for two varieties of tomatos at three planting densities.  
### Cleaning 2X  No outlier detected.
```{r}
tomato <- read.delim("http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/tomato.dat")

#Base
tomato1 <- data.frame(lapply(tomato, as.character), stringsAsFactors=FALSE)
tomatolist <- strsplit(tomato1$X.this.needs.reformatting.to.read.into.Splus,"\\,\\s|\\,|\\s")
I<-cbind(c("tomato"))
R <- cbind(c(10000))[rep(1,3), ]
X <- cbind(c(20000))[rep(1,3), ]
Z <- cbind(c(30000))[rep(1,3), ]
matrix<-cbind(I,t(R),t(X),t(Z))
for (i in 2:3)
{tomatoDataframe<-as.data.frame(tomatolist[i])
t<-t(tomatoDataframe)
tomatoDatamatrix1=matrix(unlist(t(t)))
tomatoDatamatrix1<-tomatoDatamatrix1[tomatoDatamatrix1 != ""]
matrix=rbind(matrix,tomatoDatamatrix1)}
colnames(matrix) <- matrix[1,]
matrix<-matrix[2:3,]
row.names(matrix)<-c(1,2)

#Tidyverse
df <- data.frame(matrix(ncol = 4, nrow = 2))
Dataframe<-{}
for (i in 1:2)
{x<- trimws(tomato[i+1,])
 y<- gsub("\\s+"," ", x)
 z<-strsplit(y, " ")
 X_Dataframe = as.data.frame(t(unlist(z)))
 Dataframe<-rbind(Dataframe,X_Dataframe)
}
Dataframe1<-Dataframe %>% separate(col=V2,into=c("1","2","3"),sep = ",")
Dataframe2<-Dataframe1 %>% separate(col=V3,into=c("4","5","6"),sep = ",")
Dataframe3<-Dataframe2 %>% separate(col=V4,into=c("7","8","9"),sep = ",")
colnames(Dataframe3) <- cbind(I,t(R),t(X),t(Z))
```
### Summary Table
```{r}
sensory8<-as.data.frame(Dataframe3)
data<-cbind(colnames(sensory8),t(sensory8))
class(data) <- "numeric"
g<-as_tibble(data)
g<-g[2:10,]
colnames(g)<-c("Density","Ife\\#1","PusaEarlyDwarf")
table<-g %>% group_by(Density) %>% summarize(IfeMeanYield = mean(`Ife\\#1`),PusaMeanYield = mean(PusaEarlyDwarf))
table
```
### Plot
Ife always performs better than Pusa under the 3 densities. And the larger the density is, the greater yield we get. But the gap between 20000 and 10000 is larger than that between 30000 and 20000. We guess increasing the density plays a less important role in improving the yield as the density becomes larger. 
```{r}
DF <- data.frame(Density = c("10000", "20000","30000"),
                 IfeTomato = c(table$IfeMeanYield),
                 PusaTomato = c(table$PusaMeanYield))
DFtall <- DF %>% gather(key = Tomato, value = Yield, IfeTomato:PusaTomato)
DFtall
plot<-ggplot(DFtall, aes(Tomato, Yield, fill =Density)) + geom_col(position = "dodge")
plot
```


